JMLR-14-133-3: Point-to-Point Reply

### 2014-10-28 pkg/partykit/inst/mloss/review3/p2p.tex
small touch-ups
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@631 255f4249-2263-4417-b1ea-8498779e27a7

\textbf{\textit{%
There are still some minor issues that should be fixed in the final version, which will
be sent out to Reviewer 3 for a quick confirmation.
As pointed out by Reviewer 3, partykit only provides a subset of the functionality of its
earlier cousin party. Porting the old functionality of party to the new
interface of partykit would improve its usefulness.}}

@@

Of course, we can easily copy the code of the old \texttt{party::cforest} into the
new \emph{partykit} package. However, we fail to see how this would increase usefulness
for practitioners given that \emph{party} is easily available. More importantly, this
would conflict with the view of Reviewer~2 who apparently agreed that more future
work should be devoted to this important topic.

@@

Therefore, the entire package along with its extensive documentation should be
seen as an original contribution. It supersedes the \emph{party} implementation
in all aspects with only one notable exception (\texttt{cforest}, for very good
reasons as explained below).

@@

This depends on the dimensions in which ``breadth'' is assessed. The above-mentioned
toolkits provide a large set of methods for binary and multiclass classification, regression
and clustering with a focus on SVMs.  \emph{Shark} and \emph{mlpack} also
contain implementations of tree algorithms for these situations.  Unlike
\emph{partykit}, none of the toolkits provides dedicated methods for targets
with other structures, e.g., censored data (including survival analysis), ordered
categorical regression (e.g., proportional odds models), item response theory (IRT),
paired comparisons, multivariate data with mixed types (e.g., several endpoints in a clinical study
with mixed numeric/categorical/censored measurement scales). Through the use
of nonparametric transformations (\texttt{ctree}) or parametric statistical models (\texttt{mob})
such cases can be addressed in \emph{partykit}.

@@

One example for such a ``success story'' that emerged while our revised manuscript was under review
is the \emph{vcrpart} package (\texttt{http://CRAN.R-project.org/package=vcrpart}).
This is a completely new package implementing varying coefficient trees for
ordinal 2-stage linear mixed models based on \emph{partykit} infrastructure.
By the way, apart from a few small questions about implementation
details, the \emph{vcrpart} authors apparently did not need to be in contact with us and have
been able to leverage the \emph{partykit} infrastructure based on its documentation.
Moreover, the main author of \emph{vcrpart} submitted a few bug reports
about smaller glitches in \emph{partykit} by e-mail (not the forum) that we have
subsequently fixed.

>>>>

\textbf{\textit{%
There are still some minor issues that should be fixed in the final version, which will
be sent out to Reviewer~3 for a quick confirmation.
As pointed out by Reviewer~3, partykit only provides a subset of the functionality of its
earlier cousin party. Porting the old functionality of party to the new
interface of partykit would improve its usefulness.}}

@@

Of course, we can easily copy the code of the old \texttt{party::cforest} into the
new \emph{partykit} package. However, the usefulness for the practitioner would not
really be increased by this (given that \emph{party} is easily available). More
importantly, if we take the recommendations of Reviewer~2 seriously (which we do),
then we should not just copy existing code but build new extensible infrastructure
for forests as well. If we only copy the old code now, future developments are likely
to change at least parts of the interface and thus potentially breaking full
backward compatibility. Therefore, we would much rather follow Reviewer~2 and devote
more future work to this important topic.

@@

Therefore, the entire package along with its extensive documentation should be
seen as an original contribution. It supersedes the \emph{party} implementation
in all aspects with only one notable exception (the \texttt{cforest} function,
for very good reasons as explained below).

@@

This depends on the dimensions in which ``breadth'' is assessed. The above-mentioned
toolkits provide a large set of methods for binary and multiclass classification, regression
and clustering with a focus on SVMs. Some of the packages above, e.g., \emph{Shark} and \emph{mlpack}, also
contain implementations of tree algorithms for these situations.  Unlike
\emph{partykit}, none of the toolkits provides dedicated methods for targets
with structures other than binary/multiclass/numeric. For example: censored data (including survival analysis), ordered
categorical regression (e.g., proportional odds models), item response theory (IRT),
paired comparisons, multivariate data with mixed types (e.g., several endpoints in a clinical study
with mixed numeric/categorical/censored measurement scales). Through the use
of nonparametric transformations (\texttt{ctree}) or parametric statistical models (\texttt{mob})
all of the cases above can be addressed in \emph{partykit}.

@@

One example for such a ``success story'' that emerged while our revised manuscript was under review
is the \emph{vcrpart} package (published on \texttt{http://CRAN.R-project.org/package=vcrpart}
in September).
This is a completely new package implementing varying coefficient trees for
ordinal 2-stage linear mixed models based on \emph{partykit} infrastructure.
By the way, apart from a few small questions about implementation
details, the \emph{vcrpart} authors apparently did not need to be in contact with us and have
been able to leverage the \emph{partykit} infrastructure based on its documentation.
Moreover, the main author of \emph{vcrpart} submitted a few bug reports
about smaller glitches in \emph{partykit} by e-mail (not the forum) that we have
subsequently fixed.
